Draft Report Modelleren-B

### 2021-05-27 Reports/draft_report.tex
More Folders

    After obtaining a function which calculates the cost of assigning hubs to cities, an intuitive algorithm can be made which tries to give an approximation of the combination of hubs that will result in the lowest possible amount of money that the company will have to spend when moving packages. 
    Since the intuitive algorithms are inherently less accurate than a standardized solver, the di

>>>>

    After obtaining a function which calculates the cost of assigning hubs to cities, an intuitive algorithm can be made which tries to give an approximation of the combination of hubs that will result in the lowest possible amount of money that the company will have to spend when moving packages. 
    Since the intuitive algorithms are inherently less accurate than a standardized solver, the different aspects of moving packages are split up and solved using different types of algorithms. The total process is divided into the collection from the cities to the hubs, fo
